Phylogenetics and the human microbiome.

### 2014-06-28 sbreview.tex
quantify diversity of a sample
Deleting a problematic sentence.

The parameter regime and focus of human-associated microbial research sits outside of the traditional setting for phylogenetics methods development and application; why should our community be interested in what microbial ecologists and medical researchers have done?
The answer is simple: this system is data- and question-rich.
Microbes are now primarily identified by their molecular sequences because such molecular identification is much more straightforward to do in high throughput than morphological or phenotypic characterization.
This motivates methods to organize and derive knowledge from those sequences via molecular evolution.
Indeed, microbial ecology has recently become for the most part the study of the relative abundances of various sequences derived from the environment, even if the framework for understanding between-microbe relationships includes metabolic information and other information not derived directly from sampled molecular sequences.

@@

Phylogenetic diversity (PD) measures use the structure and branch lengths of a phylogenetic tree to measure the diversity of a sample (Fig.~1).
The (unweighted) PD of a set of taxa $S$ in an unrooted phylogenetic tree is simply the total length of the branches that sit between taxa in $S$ \citep{faith1992conservation}.
It quantifies the ``amount of evolution'' contained in the evolutionary history of those taxa.
Unweighted PD has been applied to some 16S survey data \citep{lozupone2007global,costello2009bacterial} and to metagenomic reads in a set of marker genes \citep{kembel2011phylogenetic}.

>>>>

The parameter regime and focus of human-associated microbial research sits outside of the traditional setting for phylogenetics methods development and application; why should our community be interested in what microbial ecologists and medical researchers have done?
The answer is simple: this system is data- and question-rich.
Microbes are now primarily identified by their molecular sequences because such molecular identification is much more straightforward to do in high throughput than morphological or phenotypic characterization.
Indeed, microbial ecology has recently become for the most part the study of the relative abundances of various sequences derived from the environment, even if the framework for understanding between-microbe relationships includes metabolic information and other information not derived directly from sampled molecular sequences.

@@

Phylogenetic diversity (PD) measures use the structure and branch lengths of a phylogenetic tree to quantify the diversity of a sample (Fig.~1).
The (unweighted) PD of a set of taxa $S$ in an unrooted phylogenetic tree is simply the total length of the branches that sit between taxa in $S$ \citep{faith1992conservation}.
It quantifies the ``amount of evolution'' contained in the evolutionary history of those taxa.
Unweighted PD has been applied to some 16S survey data \citep{lozupone2007global,costello2009bacterial} and to metagenomic reads in a set of marker genes \citep{kembel2011phylogenetic}.
